---
title: 'Comparat: notebook'
author: "Andrea Bazzano"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{notebook}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(comparat)
```

## Things done
* Made a golem skeleton.
* Set the logo and the style of the UI.
* Set the first page of the UI.
* Added a module for loading data.
* Added basic automated tests for the loading data module.
* Add test to the loading data module:
    1. find a suitable dataset to put in a helper function and file.
* Add documentation to the loading data module
* Write the main non reactive functions for:
1. Added boxplots in plotly
3.1 t-test: find a suitable dataset to put in a helper function and file
4.1 F-test: find a suitable dataset to put in helper function and file (Box, Hunter?)
4.2 F-test: test with sd 1 = sd 2
* Add the t-test and F-test function to a singole module (compare)
* Add documentation to the functions and test the compare module
* Adapt and add the save module from calibrat
    1. change the list structure to store:
        1.1 the number of values for each group
        1.2 the mean for each group
        1.3 the sd for each group
        1.4 the calculated t
        1.5 the reference t
        1.6 the t-test p-value
        1.7 the calculated F
        1.8 the reference F
        1.9 the F-test p-value
    2. import and adapt the tests from Calibrat
    3. document the save module
* Adapt and add the report module from Calibrat
* Document the report module
* Adapt the Rmd report template from Calibrat
* Add tests to the Rmd report template
* Add validation check to the Rmd report template
* Add tests for the report module
* Put all pieces in the app_server.R

## Things to be done

* Setting of a GitHub/GitLab repository
* enable GitHub/GitLab CI/CD

* Include the app in a wider app with
- an interface for selecting how to input the data
  -- two samples with data (current app)
  -- one sample with data and values from sample for mean, sd AND n
  -- one sample with data and reference value from population mean, OR sd
  -- both data as mean1, sd1 AND n1 and mean2, sd2 AND n2.
  -- data as mean, sd AND n vs population mean OR sd
