---
title: 'Comparat: notebook'
author: "Andrea Bazzano"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{notebook}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(comparat)
```

## Things done
* Made a golem skeleton.
* Set the logo and the style of the UI.
* Set the first page of the UI.
* Added a module for loading data.
* Added basic automated tests for the loading data module.

## Things to be done
* Add test to the loading data module:
    1. find a suitable dataset to put in a helper function and file;
    2. decimal separator as .
    3. decimal separator as ,
    4. column separator as ,
    5. column separator as ;
    6. with headers
    7. without headers
* Add documentation to the loading data module
* Write the main non reactive functions for:
    1. boxplots in plotly
    2. normalised to mean = 0 boxplots in plotlye
    3. t-test
        3.1 find a suitable dataset to put in a helper function and file (Box, Hunter?)
        3.2 test with mean 1 = mean 2
        3.3 test with mean 1 > mean 2
        3.4 test with mean 2 < mean 1
        3.5 test with sd 1 = sd 2 and mean 1 > mean 2
        3.6 test with sd 1 != sd2 and mean 1 > mean 2
    4. F-test
        4.1 find a suitable dataset to put in helper function and file (Box, Hunter?)
        4.2 test with sd 1 = sd 2
        4.3 test with sd 1 > sd 2
        4.4 test with sd 1 < sd 1
* Add the t-test and F-test function to a singole module (test?)
* Add documentation to the function and test module
* Adapt and add the save module from calibrat
    1. change the list structure to store:
        1.1 the number of values for each group
        1.2 the mean for each group
        1.3 the sd for each group
        1.4 the calculated t
        1.5 the reference t
        1.6 the t-test p-value
        1.7 the calculated F
        1.8 the reference F
        1.9 the F-test p-value
    2. import and adapt the tests from Calibrat
    3. document the save module
* Adapt and add the report module from Calibrat
* Add tests for the report module
* Document the report module
* Adapt the Rmd report template from Calibrat
* Add tests to the Rmd report template
* Add validation check to the Rmd report template
* Put all pieces in the app_server.R
